---
title: "Time and motion quantitative analysis - final"
author: "Stefanie Meliss"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(message = FALSE)
options(knitr.kable.NA = '')

source(file = "03_process_data_fin.R")
library(kableExtra)
library(ggrepel)

# combine all info on observations and schools
# add observation date
df_obs <- left_join(
  # prepare data on observations
  orig_obs %>%
    mutate(
      day_start = as.POSIXct(Start_Unix, origin = "1970-01-01", tz = "Europe/London"),
      day_end = day_start + Duration_Seconds - 1,
      day_dur_m = Duration_Seconds/60, 
      day_dur_h = Duration_Seconds/3600, 
    ) %>%
    rename(
      day_dur_s = Duration_Seconds
    ) %>%
    select(Obs_Id, Pseudonym, School_name, Phase, Observer, Date, day_start, day_end, day_dur_h, day_dur_m, day_dur_s)
  ,
  # add school-level info
  orig_sch %>%
    select(-Export.ID, -Survey.ID)
) %>% 
  # add pupil hours
  mutate(
    pup_start = paste(Date, Pupil.school.day.start.time.),
    pup_end = paste(Date, Pupil.school.day.end.time),
  ) %>%
  mutate(
    pup_start = as.POSIXct(pup_start, format = "%a %m/%d/%Y %I.%M%p", tz = "Europe/London"),
    pup_end = as.POSIXct(pup_end, format = "%a %m/%d/%Y %I.%M%p", tz = "Europe/London")
  ) %>%
  select(-Pupil.school.day.start.time., -Pupil.school.day.end.time)

```

```{r df_inter}
# prepare data
df_inter <- left_join(
  # add info on schools and obs
  df_obs %>%
    select(Obs_Id, Pseudonym, Observer, School_name, pup_start, pup_end, Phase, day_start, day_end, day_dur_h, day_dur_m, day_dur_s),
  orig_inter %>%
    # process data
    mutate(
      # time vars
      time_start = as.POSIXct(Start_Unix, origin = "1970-01-01", tz = "Europe/London"),
      time_end = time_start + Duration_Seconds - 1,
      time_dur_s = Duration_Seconds,
      time_dur_m = time_dur_s/60
    ) %>%
    select(Obs_Id, Id, Dimension, Label, Code, Dim_Code, Dim_Code2, Dim_Label, Dim_Label2, time_start, time_end, time_dur_s, time_dur_m)) %>%
  # filter(Name != "None") %>%
  # process data
  mutate(
    # grouping vars
    stakeholder = Label,
    stakeholder = factor(stakeholder, levels = lvl_stake),
    # stake_group = if_else(grepl("^A[0-9]", stakeholder), "A. Pupils",
    #                       if_else(grepl("^B[0-9]", stakeholder), "B. Colleagues",
    #                               if_else(grepl("^C[0-9]", stakeholder), "C. Parents and other",
    #                                       NA)))
  ) %>%
  # filter so that minimum duration is more than 1 second
  filter(time_dur_s > 0) %>% 
  # check for and remove duplicates by selecting first observation
  group_by(Obs_Id, time_start) %>% 
  mutate(obs_idx = row_number()) %>% 
  filter(obs_idx == 1) %>% 
  select(-obs_idx) %>%
  # beauty correction
  ungroup() %>%
  arrange(Obs_Id, time_start) %>%
  as.data.frame()
```

```{r df_indiv}
# prepare data
df_indiv <- left_join(
  # add info on schools and obs
  df_obs %>%
    select(Obs_Id, Pseudonym, Observer, School_name, pup_start, pup_end, Phase, day_start, day_end, day_dur_h, day_dur_m, day_dur_s),
  orig_indiv %>%
    # process data
    mutate(
      # time vars
      time_start = as.POSIXct(Start_Unix, origin = "1970-01-01", tz = "Europe/London"),
      time_end = time_start + Duration_Seconds - 1,
      time_dur_s = Duration_Seconds,
      time_dur_m = time_dur_s/60
    ) %>%
    select(Obs_Id, Id, Dimension, Label, Code, Dim_Code, Dim_Code2, Dim_Label, Dim_Label2, time_start, time_end, time_dur_s, time_dur_m)) %>%
  # filter(Name != "None") %>%
  # process data
  mutate(
    # grouping vars
    activity = Label,
    activity = factor(activity, levels = lvl_act),
    nonwork = if_else(grepl("F1|F2", activity), "Non-work activity", NA)
  ) %>%
  # filter so that minimum duration is more than 1 second
  filter(time_dur_s > 0) %>% 
  # check for and remove duplicates by selecting first observation
  group_by(Obs_Id, time_start) %>% 
  mutate(obs_idx = row_number()) %>% 
  filter(obs_idx == 1) %>% 
  select(-obs_idx) %>%
  # beauty correction
  ungroup() %>%
  arrange(Obs_Id, time_start) %>%
  as.data.frame()
```

```{r df_loco}
# prepare data
df_loco <- left_join(
  # add info on schools and obs
  df_obs %>%
    select(Obs_Id, Pseudonym, Observer, School_name, pup_start, pup_end, Phase, day_start, day_end, day_dur_h, day_dur_m, day_dur_s),
  orig_loco %>%
    # process data
    mutate(
      # time vars
      time_start = as.POSIXct(Start_Unix, origin = "1970-01-01", tz = "Europe/London"),
      time_end = time_start + Duration_Seconds - 1,
      time_dur_s = Duration_Seconds,
      time_dur_m = time_dur_s/60
    ) %>%
    select(Obs_Id, Id, Dimension, Label, Code, Dim_Code, Dim_Code2, Dim_Label, Dim_Label2, time_start, time_end, time_dur_s, time_dur_m)) %>%
  # filter(Name != "None") %>%
  # process data
  mutate(
    # grouping vars
    location = factor(Label, levels = lvl_act)
  ) %>%
  # filter so that minimum duration is more than 1 second
  filter(time_dur_s > 0) %>% 
  # check for and remove duplicates by selecting first observation
  group_by(Obs_Id, time_start) %>% 
  mutate(obs_idx = row_number()) %>% 
  filter(obs_idx == 1) %>% 
  select(-obs_idx) %>%
  # beauty correction
  ungroup() %>%
  arrange(Obs_Id, time_start) %>%
  as.data.frame()

```

```{r df_long, results='asis'}
# combine all three dimensions
df_long <- df_inter %>% 
  bind_rows(df_indiv) %>%
  bind_rows(df_loco)%>% 
  ungroup() %>% 
  # declare levels
  mutate(
    Label = factor(Label, levels = c(lvl, "None")),
    Code = factor(Code, levels = lvl_c),
    Dimension = factor(Dimension, levels = c("Interactions", "Individual", "Location")),
    coded_bin = if_else(Label != "None", "Coded", "None")
  )


out <- bind_rows(
  df_long %>%
    group_by(Dimension) %>%
    # unique entries
    summarise(#Step = "Unique entries", 
      unique = n()) %>%
    ungroup() %>%
    # raw export
    mutate(
      raw = c(nrow(orig_inter), nrow(orig_indiv), nrow(orig_loco)),
    ) %>%
    add_row(Dimension = "Total", unique = nrow(df_long), raw = sum(c(nrow(orig_inter), nrow(orig_indiv), nrow(orig_loco)))) %>%
    mutate(
      # recording errors
      error = raw - unique
    ) %>%
    
    tidyr::pivot_longer(cols = c("raw", "error", "unique")) %>%
    mutate(value = as.character(value)) %>%
    tidyr::pivot_wider(names_from = "Dimension", values_from = "value")
  ,
  # coded entries
  bind_rows(
    full_join(df_long %>%
                group_by(Dimension, coded_bin) %>%
                summarise(n = n()) %>%
                ungroup(),
              df_long %>%
                group_by(Dimension) %>%
                summarise(nrow = n()) %>%
                ungroup()
    ) %>%
      mutate(
        p = n/nrow*100,
        c = paste0(n, " (", round(p, 1), "%)")
        ) ,
    df_long %>%
      group_by(coded_bin) %>%
      summarise(Dimension = "Total", n = n(), p = n()/nrow(.)*100) %>%
      ungroup() %>%
      mutate(c = paste0(n, " (", round(p, 1), "%)"))
  ) %>%
    tidyr::pivot_wider(id_cols = "coded_bin", names_from = "Dimension", values_from = "c") %>%
    rename(name = coded_bin)
)

# identified irregularities: check for gaps
tmp <- df_long %>%
  group_by(Pseudonym, Dimension) %>%
  arrange(time_start) %>%
  mutate(
    lag = lag(time_end),
    diff = time_start - lag - 1,
    gap = diff != 0,
    gap = if_else(is.na(gap), F, gap)
  ) %>%
  ungroup() %>% 
  group_by(Dimension) %>%
  mutate(nrow = n()) %>%
  ungroup() %>%
  filter(gap == T)

tmp <- bind_rows(
  tmp %>%
    group_by(Dimension, gap) %>% 
    summarise(
      n = n(), 
      p = n()/min(nrow) * 100, 
      unaccount = sum(diff, na.rm = T)
    ) %>%
    mutate(
      c = paste0(n, " (", round(p, 1), "%)"), 
      unaccount = as.character(as.numeric(unaccount))
    )
  ,
  tmp %>%
    group_by(gap) %>% 
    summarise(
      Dimension = "Total",
      n = n(), 
      p = n()/nrow(df_long) * 100, 
      unaccount = sum(diff, na.rm = T)
    ) %>%
    mutate(
      c = paste0(n, " (", round(p, 1), "%)"), 
      unaccount = as.character(as.numeric(unaccount))
    )
)

# combine and print
out %>%
  bind_rows(
    tmp %>%
      tidyr::pivot_wider(id_cols = "gap", names_from = "Dimension", values_from = "c") %>%
      rename(name = gap) %>%
      mutate(name = "irreg")
    ,
    tmp %>%
      tidyr::pivot_wider(id_cols = "gap", names_from = "Dimension", values_from = "unaccount") %>%
      rename(name = gap) %>%
      mutate(name = "unacc")
  ) %>%
  kable(caption = "Overview of TimeCaT observation entries by dimension and data processing step", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  add_footnote("*Note.* Data from all N = 18 was combined.", notation = "none") %>%
  print()


```

```{r df_wide}
# prepare second-by-second match of the three dimensions - X-TENDED datasets #

# INTERACTIONS #
xtd_inter <- df_inter %>%
  select(Id, Obs_Id, Pseudonym, Phase, School_name, pup_start, pup_end, Observer, time_start, time_end, time_dur_s, Label, Code, Dim_Label) %>%
  rowwise() %>%
  mutate(time_seq = list(seq(from = time_start, to = time_end, by = "1 sec"))) %>%
  tidyr::unnest(time_seq) %>%
  ungroup() %>%
  rename(
    id_stake = Id,
    time_stamp = time_seq,
    time_start_stake = time_start,
    time_end_stake = time_end,
    dur_stake = time_dur_s,
    stake = Label,
    code_stake = Code,
    dim_stake = Dim_Label
  ) %>%
  # select(-Id, -time_start, -time_end, -time_dur_s) %>%
  relocate(time_stamp) %>%
  arrange(Pseudonym, time_stamp) %>%
  # group_by(time_stamp, Observer) %>%
  # mutate(time_dur_s = n()) %>%
  # ungroup() %>%
  mutate(stake_bin = if_else(stake == "None", "None", "Interaction")) %>%
  as.data.frame()

# INDIVIDUALS #
xtd_indiv <- df_indiv %>%
  select(Id, Obs_Id, Pseudonym, Phase, School_name, pup_start, pup_end, Observer, time_start, time_end, time_dur_s, Label, Code, Dim_Label) %>%
  rowwise() %>%
  mutate(time_seq = list(seq(from = time_start, to = time_end, by = "1 sec"))) %>%
  tidyr::unnest(time_seq) %>%
  ungroup() %>%
  rename(
    id_act = Id,
    time_stamp = time_seq,
    time_start_act = time_start,
    time_end_act = time_end,
    dur_act = time_dur_s,
    act = Label,
    code_act = Code,
    dim_act = Dim_Label
  ) %>%
  # select(-Id, -time_start, -time_end, -time_dur_s) %>%
  relocate(time_stamp) %>%
  arrange(Pseudonym, time_stamp) %>%
  # group_by(time_stamp, Observer) %>%
  # mutate(time_dur_s = n()) %>%
  # ungroup() %>%
  mutate(act_bin = if_else(act == "None", "None", "Individual")) %>%
  as.data.frame()

# LOCATIONS #
xtd_loco <- df_loco %>%
  select(Id, Obs_Id, Pseudonym, Phase, School_name, pup_start, pup_end, Observer, time_start, time_end, time_dur_s, Label, Code, Dim_Label) %>%
  rowwise() %>%
  mutate(time_seq = list(seq(from = time_start, to = time_end, by = "1 sec"))) %>%
  tidyr::unnest(time_seq) %>%
  ungroup() %>%
  rename(
    id_loc = Id,
    time_stamp = time_seq,
    time_start_loc = time_start,
    time_end_loc = time_end,
    dur_loc = time_dur_s,
    loc = Label,
    code_loc = Code,
    dim_loc = Dim_Label
  ) %>%
  # select(-Id, -time_start, -time_end, -time_dur_s) %>%
  relocate(time_stamp) %>%
  arrange(Pseudonym, time_stamp) %>%
  # group_by(time_stamp, Observer) %>%
  # mutate(time_dur_s = n()) %>%
  # ungroup() %>%
  as.data.frame()

# MERGER #
df_wide <- 
  xtd_inter %>%
  full_join(xtd_indiv) %>%
  full_join(xtd_loco) %>%
  relocate(Obs_Id, Pseudonym, Observer, Phase, School_name, pup_start, pup_end, time_stamp) 

# process merged data
df_wide <- df_wide %>%
  group_by(Obs_Id, time_stamp) %>%
  mutate(time_dur_s = n()) %>%
  ungroup() %>%
  mutate(
    # fill in blanks
    act = if_else(is.na(act), "None", act),
    stake = if_else(is.na(stake), "None", stake),
    # create variable that specifies if any record is available
    no_record = stake == "None" & act == "None",
    # binarise
    indiv_bin = if_else(act == "None", 0, 1),
    inter_bin = if_else(stake == "None", 0, 1),
    # create variable representing multi-tasking
    multi = if_else(indiv_bin == 0 & inter_bin == 1, "Interaction single-task",
                    if_else(indiv_bin == 1 & inter_bin == 0, "Individual single-task",
                            if_else(indiv_bin == 1 & inter_bin == 1, "Multi-task",
                                    if_else(indiv_bin == 0 & inter_bin == 0, "No task", 
                                            NA)))),
    id_multi = if_else(indiv_bin == 0 & inter_bin == 1, id_stake,
                       if_else(indiv_bin == 1 & inter_bin == 0, id_act,
                               if_else(indiv_bin == 1 & inter_bin == 1, paste0(id_stake, "_", id_act),
                                       if_else(indiv_bin == 0 & inter_bin == 0, NA, 
                                               NA)))),
    # create variable representing domain
    task_inter = if_else(multi %in% c("Interaction single-task", "Multi-task"), "Interaction task", NA),
    task_indiv = if_else(multi %in% c("Individual single-task", "Multi-task"), "Individual task", NA),
    
    # variables for non-work activity analysis
    code_f2 = if_else(grepl("F2", act) & grepl("None|B6", stake), "F2A",
                 if_else(grepl("F2", act) & ! grepl("None|B6", stake), "F2B",
                         NA)),
    f2 = if_else(grepl("F2", act) & grepl("None|B6", stake), "F2A. Restorative food and drink activity",
                 if_else(grepl("F2", act) & ! grepl("None|B6", stake), "F2B. Non-restorative food and drink activity",
                         NA)),
    nonwork = if_else(grepl("F1", act) | grepl("F2A", f2), "Restorative non-work activity",
                      if_else(grepl("F2B", f2), "Non-restorative non-work activity",
                              NA)),
    # task finished before pupil hours
    pupil_hours = case_when(
      time_stamp < pup_start ~ "Before pupil hours",
      time_stamp >= pup_start & time_stamp <= pup_end ~ "During pupil hours",
      time_stamp > pup_end ~ "After pupil hours",
      TRUE ~ NA_character_
    )) %>%
  mutate(
    pupil_hours = factor(pupil_hours, levels = c("Before pupil hours", "During pupil hours", "After pupil hours"))
  ) %>%
  arrange(time_stamp) %>% # Replace 'order_var' with your ordering variable
  group_by(id_act) %>%
  mutate(
    # Only calculate f2_change for F2, else FALSE
    f2_change = if_else(!is.na(f2),
                        (f2 != lag(f2)) | (row_number() == 1),
                        FALSE),  
    nonwork_change = if_else(!is.na(nonwork),
                             (nonwork != lag(nonwork)) | (row_number() == 1),
                             FALSE),  
  ) %>%
  mutate(
    # Only calculate nonwork_seq for F2, else NA_integer_
    f2_seq = if_else(!is.na(f2),
                     cumsum(f2_change),
                     NA_integer_),
    nonwork_seq = if_else(!is.na(nonwork),
                          cumsum(nonwork_change),
                          NA_integer_),
    id_act_f2 = if_else(!is.na(f2),
                        stringr::str_c(id_act, "_", stringr::str_pad(f2_seq, 2, pad = "0")),
                        NA_character_),
    id_act_nonwork = if_else(!is.na(nonwork),
                             stringr::str_c(id_act, "_", stringr::str_pad(nonwork_seq, 2, pad = "0")),
                             NA_character_)
  ) %>%
  select(-f2_change, -nonwork_change, -f2_seq, -nonwork_seq) %>%
  ungroup()

```

```{r timeline, eval = FALSE, fig.height=7}
# subset data
data_ts <- df_long[df_long$Obs_Id == id & df_long$Label != "None", ]

# process
data_ts <- data_ts %>%
  # limit window
  filter(time_end > window_start & time_start < window_end) %>%
  arrange(Dimension, time_start) %>%
  mutate(
    # adjust timings to the closest value above the threshold
    time_end = if_else(time_end > window_end, 
                       # time_end[time_end > window_end][which.min(time_end[time_end > window_end] - window_end)],
                       window_end,
                       time_end),
    time_start = if_else(time_start < window_start, 
                         # time_start[time_start > window_start][which.min(time_start[time_start > window_start] - window_start)],
                         window_start,
                         time_start),
    
    # mid point for labels
    dur_new = difftime(time_end, time_start),
    time_mid = time_start + dur_new/2,
    
    # convert date time into minutes since start
    y_start = as.numeric(difftime(time_start, min(time_start), units = "mins")),
    y_end = as.numeric(difftime(time_end, min(time_start), units = "mins")),
    y_mid = as.numeric(difftime(time_mid, min(time_start), units = "mins")),
    
    # fill colour
    fill_col = if_else(Dimension != "Location", Dim_Code, Code),
  ) %>%
  group_by(Dimension) %>%
  mutate(
    side = rep(c("left", "right"), length.out = n()),
  ) %>%
  ungroup() %>%
  as.data.frame()

# Create a data_ts frame for the background (full day) box
data_bg <- data.frame(
  start = min(data_ts$time_start),
  start_y = min(data_ts$y_start),
  end = max(data_ts$time_end),
  end_y = max(data_ts$y_end)
)

p <- ggplot() + ambition_theme +
  # Grey background for the day
  geom_rect(
    data = data_bg,
    aes(xmin = .95, xmax = 1.05,  # x position for each individual
        ymin = start_y, ymax = end_y),
    fill = black10,
  ) +
  # Task rectangles
  geom_rect(
    data = data_ts,
    aes(xmin = .9, xmax = 1.1, ymin = y_start, ymax = y_end, 
        fill = fill_col), 
    colour = black, linewidth = 0.05
  ) +
  scale_fill_manual(values = fill_col) +
  scale_y_continuous(
    name = "Time",
    breaks = seq(0, 60, 5),
    limits = c(0, max(data_ts$y_end))) +
  facet_grid(cols = vars(Dimension), drop = F) +
  theme(legend.position = "none") + 
  guides(fill = guide_legend(ncol = 1)) + 
  theme(
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.title.x = element_blank(),
    axis.ticks.x = element_blank(),
    axis.text.x = element_blank(),
    # axis.text.y = element_blank()
  ) +
  coord_cartesian(xlim = c(0.5,1.5)) +
  # Labels to the left
  geom_label_repel(data = data_ts[data_ts$side == "left", ],
                   aes(x = 0.99, y = y_mid, label = Code), # Just right of xmin = 0.9
                   nudge_x = -0.25,  # Nudge left
                   hjust = 0.5, vjust = 0.5, # centres text vertically and horizontally
                   direction = "both"
  ) +
  # Labels to the right
  geom_label_repel(data = data_ts[data_ts$side == "right", ],
                   aes(x = 1.01, y = y_mid, label = Code), # Just left of xmax = 1.1
                   nudge_x = 0.25,  # Nudge right
                   hjust = 0.5, vjust = 0.5, # centres text vertically and horizontally
                   direction = "both"
  )

# # DEBUG: graphs with time of day
# p <- ggplot() + ambition_theme +
#   # Grey background for the day
#   geom_rect(
#     data = data_bg,
#     aes(xmin = .95, xmax = 1.05,  # x position for each individual
#         ymin = start, ymax = end),
#     fill = black10,
#   ) +
#   # Task rectangles
#   geom_rect(
#     data = data_ts,
#     aes(xmin = .9, xmax = 1.1, ymin = time_start, ymax = time_end, 
#         fill = fill_col), 
#     colour = black, linewidth = 0.05
#   ) +
#   scale_fill_manual(values = fill_col) +
#   scale_y_datetime(
#     name = "Time of day",
#     breaks = seq(data_bg$start, data_bg$end, by = "5 mins"),
#     date_labels = "%H:%M",
#     limits = c(data_bg$start, data_bg$end),
#     sec.axis = sec_axis(
#       # Transform: convert POSIXct to minutes since day_start
#       trans = ~ as.numeric(difftime(., data_bg$start, units = "mins")),
#       name = "Minutes since start")
#   ) +
#   facet_grid(cols = vars(Dimension)) +
#   theme(legend.position = "none") + 
#   guides(fill = guide_legend(ncol = 1)) + 
#   theme(
#     panel.grid.major.x = element_blank(),
#     panel.grid.minor.x = element_blank(),
#     axis.title.x = element_blank(),
#     axis.ticks.x = element_blank(),
#     axis.text.x = element_blank(),
#   ) +
#   coord_cartesian(xlim = c(0.5,1.5)) +
#   # Labels to the left
#   geom_label_repel(data = data_ts[data_ts$side == "left", ],
#                    aes(x = 0.95, y = time_mid, label = Code), # Just right of xmin = 0.9
#                    nudge_x = -0.25,  # Nudge left
#                    hjust = 0.5, vjust = 0.5, # centres text vertically and horizontally
#                    direction = "both"
#   ) +
#   # Labels to the right
#   geom_label_repel(data = data_ts[data_ts$side == "right", ],
#                    aes(x = 1.05, y = time_mid, label = Code), # Just left of xmax = 1.1
#                    nudge_x = 0.25,  # Nudge right
#                    hjust = 0.5, vjust = 0.5, # centres text vertically and horizontally
#                    direction = "both"
#   )

p

```

# Timeline plots

```{r figs, fig.height=7, eval = T}
# determine colours
fill_col <- c(
  navy, # A_teach
  col.tint(navy, .6), # A
  teal, # B
  black40, # C
  coral, # D
  cyan, # E
  orange, # F
  purple, # G
  blue, # TS1
  blue, # TS2
  red, # TS3
  red, # TS4
  black40, # TS5
  rep(yellow, sum(grepl("^SW[0-9]", lvl))),
  rep(yellow, sum(grepl("^SA[0-9]", lvl))),
  rep(yellow, sum(grepl("^SC[0-9]", lvl)))
)
names(fill_col) <- c(
  "A_teach", "A", "B", "C", "D", "E", "F", "G", 
  "TS1", "TS2", "TS3", "TS4", "TS5", 
  "SW1", "SW2", "SW3", "SW4", 
  "SA1", "SA2", "SA3", 
  "SC1", "SC2", "SC3", "SC4"
)

# subset data for teacher
id <- "-OmhS-f4fCg8wOO2Rx4Z"
ps <- "SST6"

# determine start and end times
window_start <- as.POSIXct("2026-03-02 11:07:00")
window_end <- as.POSIXct("2026-03-02 11:37:00")

# create plot
cat("\nFig 2\n")
<<timeline>>

# subset data for teacher
id <- "-OfT0nqTJmLp5mY8Xe7M"
ps <- "PST1"

# determine start and end times
window_start <- as.POSIXct("2025-12-02 08:02:20")
window_end <- as.POSIXct("2025-12-02 08:17:20")

# create plot
cat("\nFig 5\n")
<<timeline>>

# determine start and end times
window_start <- as.POSIXct("2025-12-02 12:48:15")
window_end <- as.POSIXct("2025-12-02 13:03:15")

# create plot
cat("\nFig 9\n")
<<timeline>>

# determine start and end times
window_start <- as.POSIXct("2025-12-02 08:47:00")
window_end <- as.POSIXct("2025-12-02 09:07:00")

# create plot
cat("\nFig 10\n")
<<timeline>>

# subset data for teacher
id <- "-OiqJf-El_Wa6Se-GG7N"
ps <- "PST4"

# determine start and end times
window_start <- as.POSIXct("2026-01-13 10:45:22")
window_end <- as.POSIXct("2026-01-13 11:05:22")

# create plot
cat("\nFig 11\n")
<<timeline>>

# determine start and end times
window_start <- as.POSIXct("2026-01-13 12:04:05")
window_end <- as.POSIXct("2026-01-13 12:44:05")

# create plot
cat("\nFig 12\n")
<<timeline>>

# subset data for teacher
id <- "-On11sXtO7bdxrct2nV8"
ps <- "SST9"

# determine start and end times
window_start <- as.POSIXct("2026-03-06 11:34:00")
window_end <- as.POSIXct("2026-03-06 12:04:00")

# create plot
cat("\nFig 13\n")
<<timeline>>

```

# Observed hours and evening hours

```{r, results='asis'}
# TOTAL LENGTH OF OBSERVED DAY #

# aggregate observation duration
data_agg <- aggregate_obs(
  data = df_obs %>%  mutate(status = T),
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("status"),
  obs_id_var = "Obs_Id",
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "day_dur_m"
)
# select cols and rename
data_agg <- data_agg[, grepl("Phase|_dur", names(data_agg))]

# print
data_agg %>%
  arrange(Phase) %>%
  kable(caption = "Average length of day observed", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  add_footnote("*Note.* Results are reported in hours.", notation = "none") %>%
  print()

# OBSERVATION PER DIMENSION 
data_agg <- bind_rows(
  # BY DIMENSION
  full_join(
    # minutes
    aggregate_obs(
      data = df_long %>% filter(Label != "None"),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dimension"),
      factor_levels = c("Whole sample", "Primary", "Secondary")
    ),
    # hours
    aggregate_obs(
      data = df_long %>% filter(Label != "None"),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dimension"),
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_m"
    )
  ),
  # COMBINE INTER & INDIV
  full_join(
    # minutes
    aggregate_obs(
      data = df_long %>% filter(Label != "None") %>% mutate(Dimension = if_else(Dimension == "Location", NA, "Tasks")),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dimension"),
      factor_levels = c("Whole sample", "Primary", "Secondary")
    ),
    # hours
    aggregate_obs(
      data = df_long %>% filter(Label != "None") %>% mutate(Dimension = if_else(Dimension == "Location", NA, "Tasks")),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dimension"),
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_m"
    )
  ) %>% filter(!is.na(Dimension))
)

# print
data_agg %>%
  arrange(Phase) %>%
  kable(caption = "Observations by domain", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  add_header_above(header = c(" " = 2, "Total counts" = 7, "Total minutes" = 7, "Total hours" = 7)) %>%
  add_footnote("*Note.* Results are reported in minutes and hours.", notation = "none") %>%
  print()

```

### **Table**
### *Descriptive statistics on the observed hours in addition to self-reported additional hours worked after observation before the next working day*

```{r, results='asis'}
# preapre evening hour data
df_eve <- orig_eve[, c("Pseudonym", "Observed.day.evening.work.estimate..mins.")]
names(df_eve)[2] <- "eve_est_min"
df_eve$eve_est_min <- ifelse(df_eve$eve_est_min == "0 as it was a Friday, but 300 on Sunday (I think this should count but open to discussion)", "300", df_eve$eve_est_min)
df_eve$eve_est_h <- lubridate::dhours(as.numeric(df_eve$eve_est_min) / 60)

# join with observed hours
data_hrs <- df_obs %>%
  mutate(day_dur_h = lubridate::dhours(as.numeric(day_dur_s) / 3600)) %>%
  full_join(., df_eve) %>%
  mutate(total_h = day_dur_h + eve_est_h)

# prepare data for aggregation
data_hrs <- tidyr::pivot_longer(
  data = data_hrs,
  cols = c("day_dur_h", "eve_est_h", "total_h"),
  names_to = "measure",
  values_to = "time_dur_s") %>%
  mutate(
    time_dur_s = as.numeric(time_dur_s),
    time_dur_m = time_dur_s/60)

# aggregate observation duration
data_agg <- 
  full_join(
    # in minutes
    aggregate_obs(
      data = data_hrs,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("measure"),
      obs_id_var = "Obs_Id",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    )
    ,
    # in hours
    aggregate_obs(
      data = data_hrs,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("measure"),
      obs_id_var = "Obs_Id",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_m"
    )
  ) %>%
  mutate(Phase = factor(Phase, levels = c("Whole sample", "Primary", "Secondary")),
         measure = if_else(measure == "eve_est_h", "Work before next working day",
                           if_else(measure == "day_dur_h", "Observed",
                                   if_else(measure == "total_h", "Total", NA)))
  )

# select cols and rename
tmp <- data_agg[, grepl("Phase|meas|_hrs", names(data_agg))]
names(tmp) <- gsub("_hrs", "", names(tmp))

# reformat 
tmp <- tmp %>%
  mutate(
    desc = paste0(round(mean, 2), " (", round(sd, 2), ") [", round(min, 2), "; ", round(max, 2), "]"),
    measure = factor(measure, levels = c("Observed", "Work before next working day", "Total"))
  ) %>%
  select(c(Phase, measure, desc)) %>%
  tidyr::pivot_wider(., 
                     id_cols = measure, 
                     names_from = Phase, 
                     values_from = desc,
                     names_glue = "{Phase}") %>%
  relocate(`Whole sample`, .after = measure)

# export
names(tmp) <- c("Working hours", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(tmp, "desc_obs_eve.csv", row.names = F)

# print to markdown
tmp %>%
  arrange(`Working hours`) %>%
  kable(caption = "Observed hours in addition to evening working hours", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  add_footnote("*Note.* Results are reported in hours.", notation = "none") %>%
  print()
```

# Stakeholder interactions

### **Figure**
### *Overview of average total minutes teachers spent engaging with stakeholders and teaching over the observed day*

```{r, results='asis'}
data_agg <- bind_rows(
  # aggregate stakeholder groups
  aggregate_obs(
    data = df_inter,
    primary_group_vars = c("Phase"),
    secondary_group_vars = c("Dim_Label"),
    factor_levels = c("Whole sample", "Primary", "Secondary")
  ) %>%
    rename(stakeholder = Dim_Label) %>%
    mutate(cat = "Interaction with stakeholder groups") %>%
    filter(!is.na(stakeholder)) 
  ,
  # teaching time tasks
  aggregate_obs(
    data = df_inter %>% filter(Dim_Code == "A"),
    primary_group_vars = c("Phase"),
    secondary_group_vars = c("Dim_Label2"),
    factor_levels = c("Whole sample", "Primary", "Secondary")
  ) %>%
    rename(stakeholder = Dim_Label2) %>%
    mutate(cat = "Pupil interactions") %>%
    filter(!is.na(stakeholder)) 
) %>% 
  mutate(stakeholder = factor(stakeholder, levels = c("A. Pupils", "B. Colleagues", "C. Parents and other", "Teaching interactions", "Other pupil interactions")))

# plot
ggplot(data = data_agg, aes(x = stakeholder, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  ambition_theme +
  # coord_cartesian(ylim = c(0, 360)) +
  facet_grid(cols = vars(cat), scales = "free_x", space = "free_x") +
  scale_fill_manual(values = c(navy, blue, red)) +
  scale_x_discrete(labels = function(x) stringr::str_wrap(stringr::str_replace_all(x, "foo" , " "),
                                                          width = 15)) +
  ylab("Minutes spent") +
  xlab("")  +
  labs(fill = "Teacher group")
cat("\n\n")
cat("*Note.* For each teacher, total minutes spent engaging with stakeholders and teaching were summed. Summary statistics were then calculated across teachers. Bars represent M whereas error bars represent SE.\n\n")
```

### **Figure**
### *Breakdown of teacher-aggregated total minutes spent in stakeholder interactions*


```{r, results='asis'}
# aggregate stakeholder interactions
data_agg <- aggregate_obs(
  data = df_inter,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("stakeholder"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(!is.na(stakeholder))

data_agg$label <- stringr::str_sub(data_agg$stakeholder, 1, 4)
data_agg$label <- gsub(" ", "", data_agg$label)
data_agg$label <- factor(data_agg$label, levels = c(paste0("A", 1:12, "."), paste0("B", 1:7, "."), paste0("C", 1:4, ".")))

# ce
a <- ggplot(data = data_agg[grepl("^A[0-9]", data_agg$stakeholder), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  # coord_cartesian(ylim = c(0, 200)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Pupil interactions")

b <- ggplot(data = data_agg[grepl("^B[0-9]", data_agg$stakeholder), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 60)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Colleague interactions")

c <- ggplot(data = data_agg[grepl("^C[0-9]", data_agg$stakeholder), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 60)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  labs(fill = "Teacher group") +
  ylab("Minutes spent") +
  xlab("Other stakeholder interactions")



ggpubr::ggarrange(a + theme(legend.position = "none"),
                  ggpubr::ggarrange(b + theme(legend.position = "none"), c + theme(legend.position = "none"), 
                                    ncol = 2, labels = c("B", "C"),
                                    font.label = list(size = 14), 
                                    widths = c(1.25, 1),
                                    vjust = 1), 
                  nrow = 2, 
                  labels = "A", 
                  font.label = list(size = 14),
                  vjust = 1,
                  common.legend = T, legend = "bottom") 
cat("\n\n")
cat("*Note.* For each teacher, total minutes spent engaging in various stakeholder interactions with pupils (A), colleagues (B) and other stakeholders (C) were summed. Summary statistics were then calculated across teachers. Bars represent M whereas error bars represent SE.\n\n")


```

### **Table**
### *Descriptive statistics on the duration of stakeholder interactions*

```{r, results='asis'}

# aggregate stakeholder interactions
data_agg <- aggregate_obs(
  data = df_inter,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("stakeholder"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(!is.na(stakeholder)) %>%
  bind_rows(
    # aggregate stakeholder groups
    aggregate_obs(
      data = df_inter,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dim_Label"),
      factor_levels = c("Whole sample", "Primary", "Secondary")
    ) %>%
      rename(stakeholder = Dim_Label) %>%
      filter(!is.na(stakeholder)) 
  ) %>%
  bind_rows(
    # teaching time tasks
    aggregate_obs(
      data = df_inter %>% filter(Dim_Code == "A"),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dim_Label2"),
      factor_levels = c("Whole sample", "Primary", "Secondary")
    ) %>%
      rename(stakeholder = Dim_Label2) %>%
      filter(!is.na(stakeholder)) 
  ) %>% 
  ungroup() %>%
  as.data.frame()

# duration
dat <- data_agg[, grepl("Phase|stakeholder|_mins", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = stakeholder, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("stakeholder", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  # pupil
  mutate(stakeholder = "Pupil interactions") %>%
  bind_rows(., dat %>% filter(grepl("^A[0-9]", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("^Teach", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("^Other", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("A. Pupils", stakeholder))) %>%
  # colleague
  bind_rows(., tmp %>% mutate(stakeholder = "Colleague interactions")) %>%
  bind_rows(., dat %>% filter(grepl("^B[0-9]", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("B. Coll", stakeholder))) %>%
  # other
  bind_rows(., tmp %>% mutate(stakeholder = "Parent and other stakeholder interactions")) %>%
  bind_rows(., dat %>% filter(grepl("^C[0-9]", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("C. Par", stakeholder)))

# export
names(out) <- c("Stakeholder interaction", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_inter_dur.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()


```


### **Table**
### *Descriptive statistics on the frequency of stakeholder interactions*

```{r, results='asis'}
# frequency
dat <- data_agg[, grepl("Phase|stakeholder|_count", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_count", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = stakeholder, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("stakeholder", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  # pupil
  mutate(stakeholder = "Pupil interactions") %>%
  bind_rows(., dat %>% filter(grepl("^A[0-9]", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("^Teach", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("^Other", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("A. Pupils", stakeholder))) %>%
  # colleague
  bind_rows(., tmp %>% mutate(stakeholder = "Colleague interactions")) %>%
  bind_rows(., dat %>% filter(grepl("^B[0-9]", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("B. Coll", stakeholder))) %>%
  # other
  bind_rows(., tmp %>% mutate(stakeholder = "Parent and other stakeholder interactions")) %>%
  bind_rows(., dat %>% filter(grepl("^C[0-9]", stakeholder))) %>%
  bind_rows(., dat %>% filter(grepl("C. Par", stakeholder)))

# export
names(out) <- c("Stakeholder interaction", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_inter_freq.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```


# Individual tasks

### **Figure**
### *Breakdown of teacher-aggregated total minutes spent conducting individual activities*

```{r, results='asis'}
# individual activities
data_agg <- aggregate_obs(
  data = df_indiv,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("activity"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(!is.na(activity))

data_agg$label <- stringr::str_sub(data_agg$activity, 1, 4)
data_agg$label <- gsub(" ", "", data_agg$label)

d <- ggplot(data = data_agg[grepl("^D[0-9]", data_agg$activity), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 50)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Individual work related to pupil learning and pastoral duties")

e <- ggplot(data = data_agg[grepl("^E[0-9]", data_agg$activity), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 40)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Other individual tasks")

f <- ggplot(data = data_agg[grepl("^F[0-9]", data_agg$activity), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 40)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  labs(fill = "Teacher group") +
  ylab("Minutes spent") +
  xlab("Non-work activity")


g <- ggplot(data = data_agg[grepl("^G[0-9]", data_agg$activity), ], aes(x = label, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 40)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  labs(fill = "Teacher group") +
  ylab("Minutes spent") +
  xlab("Motion")


ggpubr::ggarrange(d + theme(legend.position = "none"),
                  ggpubr::ggarrange(e + theme(legend.position = "none"), 
                                    f + theme(legend.position = "none"), 
                                    g + theme(legend.position = "none"), 
                                    ncol = 3, widths = c(2, 1.5, 1),
                                    labels = c("B", "C", "D"),
                                    font.label = list(size = 14), 
                                    vjust = 1), 
                  nrow = 2, 
                  labels = "A", 
                  font.label = list(size = 14),
                  vjust = 1,
                  common.legend = T, legend = "bottom") 
cat("\n\n")
cat("*Note.* For each teacher, total minutes spent engaging in various individual tasks related to pupil learning and pastorial duties (A), other individual tasks (B), recreation (C) and traveling through the school (D) were summed. Summary statistics were then calculated across teachers. Bars represent M whereas error bars represent SE.\n\n")



```

```{r, eval=F}
# aggregate
aggregate_obs(
  # rest
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("act"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
) %>% 
  filter(grepl("F1", act))

# aggregate
aggregate_obs(
  # food and drink
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("act"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
) %>% 
  filter(grepl("F2", act))


# aggregate
aggregate_obs(
  # food and drink
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("f2"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
)

# aggregate
aggregate_obs(
  # restorative non-work
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("nonwork"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
)


aggregate_obs(
  # Total non-work activity
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("dim_act"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
) %>%
  filter(grepl("F", dim_act))

```



```{r, eval=F}

# Filter F2 tasks
f2 <- df_indiv %>%
  filter(grepl("F2", Label))

# f2 %>% 
#   group_by(Pseudonym) %>% 
#   summarise(dur_mins = sum(time_dur_s)/60) %>% summarise(m = mean(dur_mins), sd = sd(dur_mins), min = min(dur_mins), max = max(dur_mins))

# add an empty row at the start of the stakeholder interactions for each ppt to have "none" from the start of the observation to the first recorded observation
tmp <- df_inter %>%
  ungroup() %>%
  select(Observer, Pseudonym, Label, Code, time_start, time_end, day_start, Id) %>%
  group_by(Pseudonym) %>%
  group_modify(~ add_row(.x, Label = "None", .before = 1)) %>%
  mutate(
    Observer = if_else(is.na(Observer), min(Observer, na.rm = T), Observer),
    time_end = if_else(is.na(time_end), min(time_start, na.rm = T), time_end),
    time_start = if_else(is.na(time_start), min(day_start, na.rm = T), time_start),
  ) %>%
  ungroup() %>%
  select(-day_start, -Pseudonym)
names(tmp) <- c("Observer", "stake", "code_stake", "time_start_stake", "time_end_stake", "Id_stake")

# combine stakeholder interaction and individual activity data
f2_stake <- fuzzyjoin::interval_left_join(
  x = f2 %>% filter(Observer == "Ryan Yung"),
  y = tmp %>% filter(Observer == "Ryan Yung"),
  by = c("time_start" = "time_start_stake", "time_end" = "time_end_stake")) %>%
  ungroup() %>%
  bind_rows(.,
            fuzzyjoin::interval_left_join(
              x = f2 %>% filter(Observer == "Rebecca Curtis"),
              y = tmp %>% filter(Observer == "Rebecca Curtis"),
              by = c("time_start" = "time_start_stake", "time_end" = "time_end_stake")) %>%
              ungroup()) %>% 
  mutate(
    overlap = compute_overlap(start1 = time_start, end1 = time_end, start2 = time_start_stake, end2 = time_end_stake),
    Observer = Observer.x) %>%
  select(-Observer.x, -Observer.y)

# f2_stake %>% 
#   select(Pseudonym, Label, time_start, time_end, time_dur_s) %>% 
#   filter(!duplicated(.)) %>% 
#   group_by(Pseudonym) %>% 
#   summarise(
#     dur_mins = sum(time_dur_s)/60) #%>% summarise(m = mean(dur_mins), sd = sd(dur_mins), min = min(dur_mins), max = max(dur_mins))
# 
# f2_stake %>% 
#   group_by(Pseudonym) %>% 
#   summarise(dur_mins = sum(overlap)/60) %>%
#   ungroup() %>%
#   tidyr::complete(Pseudonym, fill = list(dur_mins = 0))  #%>% summarise(m = mean(dur_mins), sd = sd(dur_mins), min = min(dur_mins), max = max(dur_mins))
# 
# f2_stake %>%
#   mutate(Pseudonym = factor(Pseudonym)) %>%
#   filter(grepl("B6.|None", stake)) %>%
#   group_by(Pseudonym) %>% 
#   summarise(dur_mins = sum(overlap)/60) %>%
#   ungroup() %>%
#   tidyr::complete(Pseudonym, fill = list(dur_mins = 0)) %>% summarise(m = mean(dur_mins), sd = sd(dur_mins), min = min(dur_mins), max = max(dur_mins))
# 
# f2_stake %>%
#   mutate(Pseudonym = factor(Pseudonym)) %>%
#   filter(!grepl("B6.|None", stake)) %>%
#   group_by(Pseudonym) %>% 
#   summarise(dur_mins = sum(overlap)/60) %>%
#   ungroup() %>%
#   tidyr::complete(Pseudonym, fill = list(dur_mins = 0)) %>% summarise(m = mean(dur_mins), sd = sd(dur_mins), min = min(dur_mins), max = max(dur_mins))


f2_stake <- f2_stake %>%
  mutate(Pseudonym = factor(Pseudonym)) %>% 
  filter(overlap > 0) %>%
  mutate(
    Code = if_else(grepl("B6.|None", stake), "F2A",
                   if_else(!grepl("B6.|None", stake), "F2B", Code))
  )

# restorative food and drink activity
tmp1 <- aggregate_obs(
  data = f2_stake %>% filter(Code == "F2A"),
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("Label"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "overlap"
) %>%
  filter(!is.na(Label)) %>%
  mutate(Label = "F2A. Restorative food and drink activity")

# non-restorative food and drink activity
tmp2 <- aggregate_obs(
  data = f2_stake %>% filter(Code == "F2B"),
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("Label"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "overlap"
) %>%
  filter(!is.na(Label)) %>%
  mutate(Label = "F2B. Non-restorative food and drink activity")

# Filter F1 tasks
f1_tasks <- left_join(orig_obs %>% select(Obs_Id, Observer),
                      df_indiv) %>%
  filter(grepl("F1", Label))

# f1_tasks %>% 
#   group_by(Pseudonym) %>% 
#   summarise(dur_mins = sum(time_dur_s)/60) %>% summarise(m = mean(dur_mins), sd = sd(dur_mins), min = min(dur_mins), max = max(dur_mins))

nonwork <- bind_rows(f2_stake, f1_tasks) %>%
  mutate(
    stake = if_else(is.na(stake), "None", stake),
    overlap = if_else(is.na(overlap), time_dur_s, overlap),
    rest_type = if_else(grepl("None|B6", stake), "Restorative non-work activity", "Non-restorative non-work activity")) %>%
  arrange(Pseudonym, time_start) %>%
  mutate(Pseudonym = factor(Pseudonym))

# restorative vs. non-restorative rest
tmp3 <- aggregate_obs(
  data = nonwork,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("rest_type"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "overlap"
) %>%
  filter(!is.na(rest_type)) %>%
  mutate(Label = rest_type)

# non-work activity
tmp4 <- aggregate_obs(
  data = df_indiv,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("nonwork"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(!is.na(nonwork)) %>%
  mutate(Label = nonwork)



# combine all rest data
rest <- bind_rows(tmp1,
                  tmp2) %>%
  bind_rows(., tmp3) %>%
  bind_rows(., tmp4) %>%
  mutate(activity = if_else(is.na(Label), rest_type, Label)) %>%
  relocate(activity) %>%
  select(-Label, -rest_type) %>%
  filter(activity != "Non-restorative non-work activity")

```


### **Table**
### *Descriptive statistics on the duration of individual activities*

```{r, results='asis'}
# individual activities
data_agg <- aggregate_obs(
  data = df_indiv,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("activity"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(!is.na(activity)) %>%
  bind_rows(
    # restorative and non-restorative food and drink
    aggregate_obs(
      # food and drink
      data = df_wide,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("f2"),
      obs_id_var = "id_act_f2",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    ) %>%
      rename(activity = f2) %>%
      filter(!is.na(activity))
  ) %>%
  bind_rows(
    # restorative non-work
    aggregate_obs(
      data = df_wide,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("nonwork"),
      obs_id_var = "id_act_nonwork",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    ) %>%
      rename(activity = nonwork) %>%
      filter(!is.na(activity))
  ) %>%
  bind_rows(
    # Totals
    aggregate_obs(
      data = df_indiv,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("Dim_Label"),
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    ) %>%
      rename(activity = Dim_Label) %>%
      filter(!is.na(activity))#%>%filter(grepl("F", dim_act))
  )

# duration
dat <- data_agg[, grepl("Phase|activity|_mins", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = activity, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("activity", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(activity = "Individual work related to pupil learning and pastoral duties") %>%
  bind_rows(., dat %>% filter(grepl("^D[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^D. ", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Other individual tasks")) %>%
  bind_rows(., dat %>% filter(grepl("^E[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^E. ", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Non-work activity")) %>%
  bind_rows(., dat %>% filter(grepl("^F[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Rest", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Non", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^F. ", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Motion")) %>%
  bind_rows(., dat %>% filter(grepl("^G[0-9]", activity)))


# export
names(out) <- c("Individual activity", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_indiv_dur.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```


```{r, results='asis', eval =F}
# stakeholder interactions
act <- aggregate_obs(
  data = df_indiv,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("activity"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(!is.na(activity))
names(act)[names(act) == "activity"] <- "activity"

# combine with rest data
act <- bind_rows(act, rest)

# duration
dat <- act[, grepl("Phase|activity|_mins", names(act))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = activity, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("activity", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(activity = "Individual work related to pupil learning and pastoral duties") %>%
  bind_rows(., dat %>% filter(grepl("^D[0-9]", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Other individual tasks")) %>%
  bind_rows(., dat %>% filter(grepl("^E[0-9]", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Non-work activity")) %>%
  bind_rows(., dat %>% filter(grepl("^F[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Rest", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Non", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Motion")) %>%
  bind_rows(., dat %>% filter(grepl("^G[0-9]", activity)))


# export
names(out) <- c("Individual activity", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_indiv_dur.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```

### **Table**
### *Descriptive statistics on the frequency of individual activities*

```{r, results='asis'}
# frequency
dat <- data_agg[, grepl("Phase|activity|_count", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_count", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = activity, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("activity", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(activity = "Individual work related to pupil learning and pastoral duties") %>%
  bind_rows(., dat %>% filter(grepl("^D[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^D. ", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Other individual tasks")) %>%
  bind_rows(., dat %>% filter(grepl("^E[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^E. ", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Non-work activity")) %>%
  bind_rows(., dat %>% filter(grepl("^F[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Rest", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Non", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^F. ", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Motion")) %>%
  bind_rows(., dat %>% filter(grepl("^G[0-9]", activity)))


# export
names(out) <- c("Individual activity", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_indiv_freq.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```


```{r, results='asis', eval=F}
# frequency
dat <- act[, grepl("Phase|activity|_count", names(act))]
names(dat)[c(-1, -2)] <- gsub("_count", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = activity, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("activity", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(activity = "Individual work related to pupil learning and pastoral duties") %>%
  bind_rows(., dat %>% filter(grepl("^D[0-9]", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Other individual tasks")) %>%
  bind_rows(., dat %>% filter(grepl("^E[0-9]", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Non-work activity")) %>%
  bind_rows(., dat %>% filter(grepl("^F[0-9]", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Rest", activity))) %>%
  bind_rows(., dat %>% filter(grepl("^Non", activity))) %>%
  bind_rows(., tmp %>% mutate(activity = "Motion")) %>%
  bind_rows(., dat %>% filter(grepl("^G[0-9]", activity)))

# export
names(out) <- c("Individual activity", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_indiv_freq.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```


# Location

### **Figure**
### *Breakdown of teacher-aggregated total minutes spent at various locations*


```{r, results='asis'}
# locations
data_agg <- aggregate_obs(
  data = df_loco,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("Label", "Code"),
  factor_levels = c("Whole sample", "Primary", "Secondary")
) %>%
  filter(Label != "None")

data_agg$Label <- factor(data_agg$Label, levels = lvl_loc)
data_agg$Code <- paste0(data_agg$Code, ".")


ts <- ggplot(data = data_agg[grepl("^TS", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 400)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Teaching and supervision spaces")

sw <- ggplot(data = data_agg[grepl("^SW", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 400)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Staff work and support spaces")

sa <- ggplot(data = data_agg[grepl("^SA", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 15)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Staff administration spaces")

sc <- ggplot(data = data_agg[grepl("^SC", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 15)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Shared communal spaces")



ggpubr::ggarrange(ggpubr::ggarrange(ts + theme(legend.position = "none"), 
                                    sw + theme(legend.position = "none"), 
                                    ncol = 2, widths = c(1.2, 1),
                                    labels = c("A", "B"),
                                    font.label = list(size = 14), 
                                    vjust = 1),
                  ggpubr::ggarrange(sa + theme(legend.position = "none"), 
                                    sc + theme(legend.position = "none"), 
                                    ncol = 2, widths = c(1, 1.3),
                                    labels = c("C", "D"),
                                    font.label = list(size = 14), 
                                    vjust = 1, 
                                    common.legend = T, legend = "bottom"), 
                  nrow = 2) 
cat("\n\n")
cat("*Note.* For each teacher, total minutes spent at various locations were summed. This includes teaching and supervision spaces (A), staff work and support spaces (B), staff administration spaces (C) and shared communal spaces (D). Summary statistics were then calculated across teachers. Bars represent M whereas error bars represent SE.\n\n")

```


### **Table**
### *Descriptive statistics on the time spent in various locations*

```{r, results='asis'}
# # locations
# loc <- aggregate_obs(
#   data = df_loco,
#   primary_group_vars = c("Phase"),
#   secondary_group_vars = c("Label"),
#   factor_levels = c("Whole sample", "Primary", "Secondary")
# )  %>%
#   filter(Label != "None") %>%
#   mutate(Label = factor(Label, levels = lvl_loc)) %>%
#   arrange(Phase, Label)
# 
# 
# duration
dat <- data_agg[, grepl("Phase|Label|_mins", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = Label, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("Label", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(Label = "Teaching and supervision spaces") %>%
  bind_rows(., dat %>% filter(grepl("^TS", Label))) %>%
  bind_rows(., tmp %>% mutate(Label = "Staff work and support spaces")) %>%
  bind_rows(., dat %>% filter(grepl("^SW[0-9]", Label))) %>%
  bind_rows(., tmp %>% mutate(Label = "Staff administration spaces")) %>%
  bind_rows(., dat %>% filter(grepl("^SA[0-9]", Label))) %>%
  bind_rows(., tmp %>% mutate(Label = "Shared communal spaces")) %>%
  bind_rows(., dat %>% filter(grepl("^SC[0-9]", Label)))

# export
names(out) <- c("Label", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_loco_dur.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```

### **Table**
### *Descriptive statistics on the frequency of being at various locations*

```{r, results='asis'}
# frequency
dat <- data_agg[, grepl("Phase|Label|_count", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_count", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = Label, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("Label", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(Label = "Teaching and supervision spaces") %>%
  bind_rows(., dat %>% filter(grepl("^TS", Label))) %>%
  bind_rows(., tmp %>% mutate(Label = "Staff work and support spaces")) %>%
  bind_rows(., dat %>% filter(grepl("^SW[0-9]", Label))) %>%
  bind_rows(., tmp %>% mutate(Label = "Staff administration spaces")) %>%
  bind_rows(., dat %>% filter(grepl("^SA[0-9]", Label))) %>%
  bind_rows(., tmp %>% mutate(Label = "Shared communal spaces")) %>%
  bind_rows(., dat %>% filter(grepl("^SC[0-9]", Label)))

# export
names(out) <- c("Label", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_loco_freq.csv", row.names = F)

# print
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```




# Multitasking

```{r, results='asis'}
# aggregate
data_agg <- aggregate_obs(
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("multi"),
  obs_id_var = "id_multi", # does not work correctly for count of "no task"
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
)  %>%
  bind_rows(
    aggregate_obs(
      data = df_wide,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("task_inter"),
      obs_id_var = "id_stake",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    )  %>%
      rename(multi = task_inter) %>%
      filter(!is.na(multi))
  ) %>%
  bind_rows(
    aggregate_obs(
      data = df_wide,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("task_indiv"),
      obs_id_var = "id_act",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    )  %>%
      rename(multi = task_indiv) %>%
      filter(!is.na(multi))
  )

# duration
dat <- data_agg[, grepl("Phase|multi|_mins", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = multi, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("multi", "Whole sample", "Primary", "Secondary")]

# export
names(dat) <- c("", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(dat, "desc_multi.csv", row.names = F)

# print
dat %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  print()

```


```{r, eval = F}
tmp_int <- df_inter %>%
  ungroup() %>%
  select(Observer, Pseudonym, Label, Code, time_start, time_end, time_dur_s, Id)
names(tmp_int) <- c("Observer", "pseudo_stake", "stake", "code_stake", "time_start_stake", "time_end_stake", "dur_stake", "Id_stake")


tmp_ind <- df_indiv %>%
  ungroup() %>%
  select(Observer, Pseudonym, Label, Code, time_start, time_end, time_dur_s, Id)
names(tmp_ind) <- c("Observer", "pseudo_act", "act", "code_act", "time_start_act", "time_end_act", "dur_act", "Id_act")

# combine stakeholder interaction and individual activity data
multi <- fuzzyjoin::interval_full_join(
  x = tmp_int %>% filter(Observer == "Ryan Yung"),
  y = tmp_ind %>% filter(Observer == "Ryan Yung"),
  by = c("time_start_stake" = "time_start_act", "time_end_stake" = "time_end_act")) %>%
  ungroup() %>%
  bind_rows(.,
            fuzzyjoin::interval_full_join(
              x = tmp_int %>% filter(Observer == "Rebecca Curtis"),
              y = tmp_ind %>% filter(Observer == "Rebecca Curtis"),
              by = c("time_start_stake" = "time_start_act", "time_end_stake" = "time_end_act")) %>%
              ungroup()) %>% 
  mutate(
    # compute overlap
    overlap = compute_overlap(start1 = time_start_stake, end1 = time_end_stake, start2 = time_start_act, end2 = time_end_act),
    # overlap no NAs 
    overlap_comp = if_else(is.na(overlap) & is.na(act), dur_stake,
                           if_else(is.na(overlap) & is.na(stake), dur_act,
                                   overlap)),
    # overlap using interaction durations for all cases where there is no overlap
    overlap_comp = if_else(is.na(overlap) & is.na(act), dur_stake,
                           if_else(is.na(overlap) & is.na(stake), dur_act,
                                   overlap)),
    # fill in the blanks
    Observer.x = if_else(is.na(Observer.x), Observer.y, Observer.x),
    Observer.y = if_else(is.na(Observer.y), Observer.x, Observer.y),
    pseudo_act = if_else(is.na(pseudo_act), pseudo_stake, pseudo_act),
    pseudo_stake = if_else(is.na(pseudo_stake), pseudo_act, pseudo_stake),
    act = if_else(is.na(act), "None", act),
    stake = if_else(is.na(stake), "None", stake),
    # create variable that specifies if any record is available
    no_record = stake == "None" & act == "None",
    # harmonise ID vars
    Observer = Observer.x,
    Pseudonym = pseudo_stake,
    Phase = if_else(grepl("PST", Pseudonym), "Primary", "Secondary")
  ) %>%
  select(-Observer.x, -Observer.y, -pseudo_act, -pseudo_stake) %>%
  mutate(
    indiv_bin = if_else(act == "None", 0, 1),
    inter_bin = if_else(stake == "None", 0, 1),
    # create variable representing multi-tasking
    multi = if_else(indiv_bin == 0 & inter_bin == 1, "Interaction single-task",
                    if_else(indiv_bin == 1 & inter_bin == 0, "Individual single-task",
                            if_else(indiv_bin == 1 & inter_bin == 1, "Multi-task",
                                    if_else(indiv_bin == 0 & inter_bin == 0, "No task", 
                                            NA))))
  )


multi <- multi %>%
  group_by(Id_stake) %>%
  mutate(
    n_stake = n(),
    # compute total overlap
    tot_ovlp_stake = sum(overlap, na.rm = T),
    # compare against recorded duration: positive numbers mean that not the whole task is covered
    diff_stake = dur_stake - tot_ovlp_stake,
    check_stake = diff_stake == 0
  ) %>%
  ungroup() %>%
  group_by(Id_act) %>%
  mutate(
    n_act = n(),
    # compute total overlap
    tot_ovlp_act = sum(overlap, na.rm = T),
    # compare against recorded duration: positive numbers mean that not the whole task is covered
    diff_act = dur_act - tot_ovlp_act,
    check_act = diff_act == 0
  ) %>%
  ungroup()

multi %>% 
  group_by(n_act, multi) %>%
  summarise(n = n())

# These are pure individual single-tasks that were conducted entirely without a concurrent interaction
multi %>%
  filter(n_act == 1) %>% # merger resulted in one row only
  filter(multi == "Individual single-task") %>% # and the only overlap found is with "none"
  # then dur_act and overlap should be equal
  mutate(check = overlap_comp == dur_act) %>%
  filter(check == F)

multi %>%
  group_by(multi, check_act) %>%
  summarise(n = n())



multi %>% 
  group_by(n_stake, multi) %>%
  summarise(n = n())

# These are pure interaction single-tasks that were conducted entirely without a concurrent individual task
multi %>%
  filter(n_stake == 1) %>% # merger resulted in one row only
  filter(multi == "Interaction single-task") %>% # and the only overlap found is with "none"
  # then dur_stake and overlap should be equal
  mutate(check = overlap_comp == dur_stake) %>%
  filter(check == F) 


# deal with cases were overlap is zero
multi %>% 
  filter(overlap == 0) %>%
  group_by(multi, n_act) %>%
  summarise(n = n())

multi <- multi %>%
  mutate(
    
    time_measure = 
      if_else(overlap == 0 & multi == "Interaction single-task", dur_stake,
              if_else(overlap == 0 & multi == "Individual single-task", dur_act,
                      overlap_comp))
    
  )

# aggregate
dat <- aggregate_obs(
  data = multi,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("multi"),
  # factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "overlap"
)  %>%  
  arrange(Phase)


# aggregate over "no records"
aggregate_obs(
  data = multi,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("no_record"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "overlap"
)  %>%
  arrange(Phase) %>%
  select(Phase, no_record, contains("_mins")) %>%
  kable(caption = "Total minutes for which there were records vs. not") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  print()

# check teacher-level data
multi %>%
  group_by(Observer, Pseudonym, no_record) %>%
  summarise(dur_mins = sum(overlap, na.rm = T)/60) %>%
  ungroup() %>%
  filter(no_record == T) %>%
  arrange(Pseudonym) %>%
  tidyr::complete(Pseudonym, fill = list(dur_mins = 0)) %>% 
  kable(caption = "Total minutes per teacher where neither an interaction nor an individual task was recorded") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  print()






```


# Task-switching

```{r, results = 'asis'}
# create df for this analysis
df_tmp <- df_long %>%
  filter(Dimension != "Location") %>%
  group_by(Pseudonym) %>%
  arrange(time_start) %>%
  # combine variable levels for individual and stakeholder tasks
  mutate(task = Label) %>%
  filter(task != "None") %>%
  # Identify task-switches
  mutate(
    prev_task = lag(task),
    next_task = lead(task),
    time_end_prev = lag(time_end),
    time_start_next = lead(time_start)
  ) %>%
  # Calculate the time gaps
  mutate(
    gap_A_to_B_secs = as.numeric(difftime(time_start, time_end_prev, units = "secs")),
    gap_B_to_A_secs = as.numeric(difftime(time_start_next, time_end, units = "secs"))
  ) %>%
  ungroup() %>%
  as.data.frame()

# A task-switch is when:
# prev_task == next_task AND task_description != prev_task (i.e., switched away and back)
df_tmp <- df_tmp %>%
  filter(
    !is.na(prev_task) & !is.na(next_task),
    prev_task == next_task, # A ... B ... A
    task != prev_task # B ≠ A
  ) %>%
  filter( # teacher stopping Task A, moving to Task B, and then returning directly to Task A, with less than a one-minute gap between each task
    gap_A_to_B_secs <= 60 & gap_B_to_A_secs <= 60
  ) %>%
  filter(
    time_dur_s < 60*10
  ) %>%
  mutate(task_swith = T)

# teacher-level aggregates
tmp <- aggregate_obs(
  data = df_tmp,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("task_swith"),
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  return_teacher_level = T,
  id_vars = c("Pseudonym", "day_dur_h")
) %>%
  rename(per_day = count) %>%
  mutate(per_hour = per_day / day_dur_h)

# sample level aggregates
data_agg <- bind_rows(
  # aggregate by phase
  tmp %>%
  group_by(Phase, .drop = FALSE) %>%
  summarise(
    across(
      .cols = c(per_day, per_hour),
      .fns = list(
        mean = ~mean(.x, na.rm = TRUE),
        sd = ~sd(.x, na.rm = TRUE),
        min = ~min(.x, na.rm = TRUE),
        max = ~max(.x, na.rm = TRUE),
        SE = ~sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))
      ),
      .names = "{.fn}_{.col}"
    ),
    .groups = "drop"
  )
  ,
  # aggregate across all
  tmp %>%
  summarise(
    across(
      .cols = c(per_day, per_hour),
      .fns = list(
        mean = ~mean(.x, na.rm = TRUE),
        sd = ~sd(.x, na.rm = TRUE),
        min = ~min(.x, na.rm = TRUE),
        max = ~max(.x, na.rm = TRUE),
        SE = ~sd(.x, na.rm = TRUE) / sqrt(sum(!is.na(.x)))
      ),
      .names = "{.fn}_{.col}"
    ),
    .groups = "drop"
  ) %>%
  mutate(Phase = "Whole sample")
) %>%
  mutate(Phase = factor(Phase, levels = c("Whole sample", "Primary", "Secondary"))) %>%
  relocate(Phase) %>%
  arrange(Phase)

# print to markdown
data_agg %>%
  kable(caption = "Count of interruptions per day and per hour", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  print()

# compute average timing of the 'in-between' tasks
df_tmp %>% 
  summarise(
    mean_mins = mean(time_dur_s, na.rm = T)/60,
    sd_mins = sd(time_dur_s, na.rm = T)/60,
    min_mins = min(time_dur_s, na.rm = T)/60,
    max_mins = max(time_dur_s, na.rm = T)/60,
  ) %>%
  kable(caption = "Duration of between tasks", digits = 2) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  print()

```



# Appendix

## Time and location of work-related conversations

```{r, results='asis'}
# create df for this analysis
df_tmp <- df_wide %>% 
  # work conversations 
  filter(code_stake == "B4") %>% 
  group_by(id_stake) %>% 
  mutate(
    # check if it fits into the pupil hour categories
    count_time = length(unique(pupil_hours)),
    # check if it took place at more than one location
    count_loc = length(unique(loc, na.rm = T)),
  ) %>%
  ungroup() %>%
  # only use the ones that fit into one time categoty
  filter(count_time == 1) %>%
  # update location
  mutate(loc2 = if_else(count_loc == 1, loc, "TS6. More than one location"))

# check count of work conversations
# df_wide %>% filter(code_stake == "B4") %>% summarise(n = length(unique(id_stake)))
# check count after removal
# df_tmp %>% summarise(n = length(unique(id_stake)))

# aggregate data based on timing #
data_agg <- aggregate_obs(
  data = df_tmp,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("pupil_hours"),
  obs_id_var = "id_stake",
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
) 

# create plot
ggplot(data = data_agg, aes(x = pupil_hours, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  ambition_theme +
  coord_cartesian(ylim = c(0, 25)) +
  scale_fill_manual(values = c(navy, blue, red)) +
  ylab("Minutes spent") +
  xlab("Timing of work conversations")  +
  labs(fill = "Teacher group")
cat("\n\n")
cat("*Note.* For each teacher, total minutes spent engaging in work-related conversations with colleagues were summed. Summary statistics were then calculated across teachers. Bars represent M whereas error bars represent SE.\n\n")

# duration
dat <- data_agg[, grepl("Phase|pupil|_mins", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = pupil_hours, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("pupil_hours", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(pupil_hours = "Duration") %>%
  bind_rows(., dat)

# frequency
dat <- data_agg[, grepl("Phase|pupil|_count", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_count", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = pupil_hours, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("pupil_hours", "Whole sample", "Primary", "Secondary")]


out <- out %>% 
  bind_rows(., tmp %>%
              mutate(pupil_hours = "Frequency")) %>%
  bind_rows(., dat)

# export
names(out) <- c("Timing", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_B4_time.csv", row.names = F)

# print to markdown
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

# aggregate data based on location #
data_agg <- aggregate_obs(
  data = df_tmp,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("loc2"),
  obs_id_var = "id_stake",
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
) %>%
  mutate(
    Code = stringr::str_sub(loc2, 1, 4),
    loc2 = factor(loc2, levels = c(lvl_loc, "TS6. More than one location"))
  )


# create plot
ts <- ggplot(data = data_agg[grepl("^TS", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 20)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Teaching and supervision spaces")

sw <- ggplot(data = data_agg[grepl("^SW", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 20)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Staff work and support spaces")

sa <- ggplot(data = data_agg[grepl("^SA", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 5)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Staff administration spaces")

sc <- ggplot(data = data_agg[grepl("^SC", data_agg$Code), ], aes(x = Code, y = mean_mins, fill = Phase)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean_mins - SE_mins, ymax = mean_mins + SE_mins), width = 0.1, position = position_dodge(0.9)
  ) +
  coord_cartesian(ylim = c(0, 5)) +
  ambition_theme +
  scale_fill_manual(values = c(navy, blue, red)) +
  labs(fill = "Teacher group") +
  theme(plot.margin = margin(1, 2, 2, 2)) +
  theme(axis.title = element_text(face = "plain")) +
  ylab("Minutes spent") +
  xlab("Shared communal spaces")



ggpubr::ggarrange(ggpubr::ggarrange(ts + theme(legend.position = "none"), 
                                    sw + theme(legend.position = "none"), 
                                    ncol = 2, widths = c(1.2, 1),
                                    labels = c("A", "B"),
                                    font.label = list(size = 14), 
                                    vjust = 1),
                  ggpubr::ggarrange(sa + theme(legend.position = "none"), 
                                    sc + theme(legend.position = "none"), 
                                    ncol = 2, widths = c(1, 1.3),
                                    labels = c("C", "D"),
                                    font.label = list(size = 14), 
                                    vjust = 1, 
                                    common.legend = T, legend = "bottom"), 
                  nrow = 2) 
cat("\n\n")
cat("*Note.* For each teacher, total minutes conversing with colleagues at various locations were summed. This includes teaching and learning spaces (A), pastoral and administrative spaces (B), staff and meeting spaces (C) and shared and communal areas (D). Summary statistics were then calculated across teachers. Bars represent M whereas error bars represent SE.\n\n")

# duration
dat <- data_agg[, grepl("Phase|loc|_mins", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_mins", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = loc2, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("loc2", "Whole sample", "Primary", "Secondary")]

tmp <- dat[1, ]
tmp[, 1:4] <- NA

out <- tmp %>% 
  mutate(loc2 = "Duration") %>%
  bind_rows(., dat)

# frequency
dat <- data_agg[, grepl("Phase|loc|_count", names(data_agg))]
names(dat)[c(-1, -2)] <- gsub("_count", "", names(dat)[c(-1, -2)] )
dat$desc <- paste0(round(dat$mean, 2), " (", round(dat$sd, 2), ") [", round(dat$min, 2), "; ", round(dat$max, 2), "]")

dat <- tidyr::pivot_wider(dat, 
                          id_cols = loc2, 
                          names_from = Phase, 
                          values_from = desc,
                          names_glue = "{Phase}")

dat <- dat[, c("loc2", "Whole sample", "Primary", "Secondary")]


out <- out %>% 
  bind_rows(., tmp %>%
              mutate(loc2 = "Frequency")) %>%
  bind_rows(., dat)

# export
names(out) <- c("Location", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_B4_loc.csv", row.names = F)

# print to markdown
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```


## Estimated vs. observed time

```{r, results='asis'}
# aggregate observed individual tasks #
data_agg <- aggregate_obs(
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("stake", "code_stake"),
  obs_id_var = "id_stake",
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s"
) %>%
  rename(
    observation = stake,
    Code = code_stake
  ) %>%
  filter(observation != "None") %>%
  # aggregate observed stakeholder interactions #
  bind_rows(
    # individual activities: all but food and drink
    data_agg <- aggregate_obs(
      data = df_wide %>% filter(code_act != "F2"),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("act", "code_act"),
      obs_id_var = "id_act",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    ) %>%
  rename(
    observation = act,
    Code = code_act
  ) %>%
  filter(observation != "None")
  ) %>%
  bind_rows(
    # restorative and non-restorative food and drink
    aggregate_obs(
      data = df_wide,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("f2", "code_f2"),
      obs_id_var = "id_act_f2",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s"
    ) %>%
  rename(
    observation = f2,
    Code = code_f2
  ) %>%
  filter(observation != "None")
  ) %>%
  # combine with survey lookup
  left_join(lookup_survey_task_map, by = "Code") %>%
  filter(!is.na(survey_item))

#### ------------ ####
# aggregate observed individual tasks #
teach_agg_obs <- aggregate_obs(
  data = df_wide,
  primary_group_vars = c("Phase"),
  secondary_group_vars = c("stake", "code_stake"),
  obs_id_var = "id_stake",
  factor_levels = c("Whole sample", "Primary", "Secondary"),
  duration_var = "time_dur_s",
  return_teacher_level = T
) %>%
  rename(
    observation = stake,
    Code = code_stake
  ) %>%
  filter(observation != "None") %>%
  # aggregate observed stakeholder interactions #
  bind_rows(
    # individual activities: all but food and drink
    data_agg <- aggregate_obs(
      data = df_wide %>% filter(code_act != "F2"),
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("act", "code_act"),
      obs_id_var = "id_act",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s",
      return_teacher_level = T
    ) %>%
  rename(
    observation = act,
    Code = code_act
  ) %>%
  filter(observation != "None")
  ) %>%
  bind_rows(
    # restorative and non-restorative food and drink
    aggregate_obs(
      data = df_wide,
      primary_group_vars = c("Phase"),
      secondary_group_vars = c("f2", "code_f2"),
      obs_id_var = "id_act_f2",
      factor_levels = c("Whole sample", "Primary", "Secondary"),
      duration_var = "time_dur_s",
      return_teacher_level = T
    ) %>%
  rename(
    observation = f2,
    Code = code_f2
  ) %>%
  filter(observation != "None")
  ) %>%
  # aggregate by survey item
  left_join(lookup_survey_task_map) %>%
  filter(!is.na(survey_item)) %>%
  group_by(Pseudonym, Phase, survey_item) %>%
  summarise(
    Observed = sum(dur)
  ) %>%
  ungroup() %>%
  tidyr::complete(tidyr::nesting(Phase, Pseudonym), survey_item, fill = list(Observed = 0))


# survey data
teach_agg_est <- df_survey %>%
  select(Pseudonym, School_code, Phase, all_of(time_cols)) %>%
  tidyr::pivot_longer(
    cols = time_cols,
    names_to = "survey_item",
    values_to = "Estimated"
  ) %>%
    left_join(lookup_survey_task_map)

teach_agg <- 
  # combine data
  full_join(teach_agg_est, teach_agg_obs) %>%
  mutate(
    # compute difference
    Difference = Estimated - Observed,
    # fix names
    survey_item = gsub("_time", "", survey_item)) %>%
  # convert to long format to plot individual data
  tidyr::pivot_longer(
    cols = c("Observed", "Estimated", "Difference"),
    names_to = "Measure",
    values_to = "total_min"
  ) 

# compute sample aggregates
data_agg <- teach_agg %>% 
  group_by(Phase, survey_item, Survey_code, Measure) %>%
  summarise(
    mean = mean(total_min),
    sd = sd(total_min),
    min = min(total_min),
    max = max(total_min),
    SE = sd(total_min) / sqrt(n())
  ) %>%
  bind_rows(., 
            teach_agg %>% 
              group_by(survey_item, Survey_code, Measure) %>%
              summarise(
                Phase = "Whole sample",
                mean = mean(total_min),
                sd = sd(total_min),
                min = min(total_min),
                max = max(total_min),
                SE = sd(total_min) / sqrt(n())
              )
  ) %>%
  ungroup() %>%
  mutate(
    Phase = factor(Phase, levels = c("Whole sample", "Primary", "Secondary")),
    Survey_code = paste0(Survey_code, "."),
    Survey_code = factor(Survey_code, levels = c(paste0("S", 1:11, ".")))
  )

# plot sample average data
ggplot(data = data_agg[data_agg$Measure != "Difference", ], aes(x = Survey_code, y = mean, fill = Measure)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(
    aes(ymin = mean - SE, ymax = mean + SE), width = 0.1, position = position_dodge(0.9)
  ) +
  ambition_theme +
  facet_wrap(vars(Phase), ncol = 1) +
  scale_fill_manual(values = c(coral, teal))  + 
  xlab("Task") +
  ylab("Minutes spent")


# duration
dat <- data_agg %>%
  arrange(Phase, Survey_code) %>%
  mutate(
    Task = paste(Survey_code, stringr::str_to_sentence(gsub("_", "/", survey_item))),
    desc = paste0(round(mean, 2), " (", round(sd, 2), ") [", round(min, 2), "; ", round(max, 2), "]") 
  ) %>%
  relocate(Task) %>%
  tidyr::pivot_wider(., 
                     id_cols = c(Task, Measure, Survey_code), 
                     names_from = Phase, 
                     values_from = desc,
                     names_glue = "{Phase}") %>%
  mutate(Measure = factor(Measure, levels = c("Estimated", "Observed", "Difference"))) %>%
  arrange(Survey_code, Measure) %>%
  select(-Survey_code)

# format output
tmp <- dat[1, ]
tmp[, 1:5] <- NA

out <- tmp %>% 
  mutate(Measure = "S1. Teaching  [~ A1, A2, A3, A5 and A6]") %>%
  bind_rows(., dat %>% filter(Task == "S1. Teaching")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S2. Managing pupil behaviour [~ A7]")) %>%
  bind_rows(., dat %>% filter(Task == "S2. Behaviour")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S3. Managing pupil transitions [~ A4]")) %>%
  bind_rows(., dat %>% filter(Task == "S3. Transitions")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S4. Assessment [~ D3]")) %>%
  bind_rows(., dat %>% filter(Task == "S4. Assessment")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S5. Marking [~ D2]")) %>%
  bind_rows(., dat %>% filter(Task == "S5. Marking")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S6. Pastoral support [~ A8 and A9]")) %>%
  bind_rows(., dat %>% filter(Task == "S6. Pastoral")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S7. Planning lessons/managing resources [~ D1]")) %>%
  bind_rows(., dat %>% filter(Task == "S7. Planning/resources")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S8. Administrative tasks [~ A12, D4 and D5]")) %>%
  bind_rows(., dat %>% filter(Task == "S8. Admin")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S9. Engaging with colleagues [~ B1, B2, B3, B4, B5 and B6]")) %>%
  bind_rows(., dat %>% filter(Task == "S9. Colleagues")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S10. Rest [~ F1 and F2A]")) %>%
  bind_rows(., dat %>% filter(Task == "S10. Rest")) %>%
  bind_rows(., tmp %>% mutate(Measure = "S11. Travelling around premises [~ G1]")) %>%
  bind_rows(., dat %>% filter(Task == "S11. Travel")) %>%
  select(-Task)

# export
names(out) <- c( "", "Whole sample (N = 18)", "Primary teachers (n = 9)", "Secondary teachers (n = 9)")
write.csv(out, "desc_est_obs.csv", row.names = F)

# print to markdown
idx <- which(is.na(out$`Whole sample (N = 18)`))

out %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), fixed_thead = T, full_width = F, position = "left") %>%
  row_spec(idx, bold = T) %>%
  print()

```

